Example Paper

### 2021-09-28 latex-article/article.tex
Fix tabularx problem
Update article and slides

% \maketitle info
\title{Example Paper}
\author{
    \href{https://kylebutts.com/}{Kyle Butts}\thanks{University of Colorado, Boulder. Email: \href{mailto:buttskyle96@gmail.com}{buttskyle96@gmail.com}.} % and Other Author
}
\date{\today}

@@

    \par~\par\noindent
    JEL-Classification: 
    \par\noindent
    Keywords: 
    \par
\end{abstract}

@@

\begin{table}[tb] 
    \caption{Summary Statistics (tabularx)}
    \label{tab:summ_stat}

@@

\begin{table}[tb] 
    \caption{Regression Results (Custom tabularx widths)} 
    \label{tab:reg1}

    \begin{adjustbox}{center}
        \begin{threeparttable}
            \begin{tabular}{\textwidth}{@{} 
                    >{\hsize=.6\hsize}L >{\hsize=.4\hsize}R >{\hsize=.4\hsize}R 
                @{}}

>>>>

% \maketitle info
\title{Example Paper}
\author{
    Author One\thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.} \ and Author Two\thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.}
}
\date{\today}

@@

    \par~\par\noindent
    {\color{asher}JEL-Classification:} ...
    \par\noindent
    {\color{asher}Keywords:} ...
    \par\vspace{-2.5mm}
\end{abstract}

@@

\begin{table}[tb] 
    \caption{Table Too Narrow (tabularx)}
    \label{tab:summ_stat}

@@

\begin{table}[tb] 
    \caption{Regression Results} 
    \label{tab:reg1}

    \begin{adjustbox}{center}
        \begin{threeparttable}
            \begin{tabular}{@{} 
                    lrr
                @{}}
